Conflict-Free Vertex Coloring of Planar Graphs

### 2017-04-10 presentation/presentation.tex
Finishing IEDS algorithm example for presentation

\algdef{SE}[FOR]{CFOR}{ENDFOR}%
   [2][default]{\ColorLine\algorithmicfor\ #2\ \algorithmicdo\ALG@compatcomm{#1}}%
   {\algorithmicend\ \algorithmicfor}%
\algdef{S}[FOR]{CFORALL}%
   [2][default]{\ColorLine\algorithmicforall\ #2\ \algorithmicdo\ALG@compatcomm{#1}}%
\algdef{SE}[LOOP]{CLOOP}{ENDLOOP}%
   [1][default]{\ColorLine\algorithmicloop\ALG@compatcomm{#1}}%
   {\algorithmicend\ \algorithmicloop}%
\algdef{SE}[REPEAT]{CREPEAT}{UNTIL}%
   [1][default]{\ColorLine\algorithmicrepeat\ALG@compatcomm{#1}}%
   [1]{\algorithmicuntil\ #1}%
\algdef{SE}[IF]{CIF}{ENDIF}%
   [2][default]{\ColorLine\algorithmicif\ #2\ \algorithmicthen\ALG@compatcomm{#1}}%
   {\algorithmicend\ \algorithmicif}%
\algdef{C}[IF]{IF}{CELSIF}%
   [2][default]{\ColorLine\algorithmicelse\ \algorithmicif\ #2\ \algorithmicthen\ALG@compatcomm{#1}}%
\algdef{Ce}[ELSE]{IF}{CELSE}{ENDIF}%
   [1][default]{\ColorLine\algorithmicelse\ALG@compatcomm{#1}}%
\makeatother
\algtext*{EndWhile}%

@@

    \only<1>{
      \begin{columns}
        \begin{column}{0.5\textwidth}
          \begin{algorithm}[H]
            \caption*{\textbf{Algorithm} IEDS}
            \scriptsize
            \begin{algorithmic}[1]
            \State $i \gets 1$
            \State Remove all isolated paths from $G$
            \While{$G$ is not empty}
              \State $D \gets \emptyset$
              \ForAll{components of $G$}
                \State Pick any vertex $v$
                \State $D \gets D \cup \{ v \}$
                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
                  \State Pick $u$ at distance 3 from some vertex in $D$
                  \State $D \gets D \cup \{ w \}$
                \EndWhile
                \ForAll{$u \in D$}
                  \State Color $u$ with color $i$
                \EndFor
                \State $i \gets i + 1$
                \ForAll{$u \in D$}
                  \State Remove $N(u)$ from $G$
                \EndFor
                \State Remove all isolated paths from G
              \EndFor
            \EndWhile
            \State Color all removed isolated paths using color $i$
            \end{algorithmic}
          \end{algorithm}
        \end{column}
        \begin{column}{0.5\textwidth}
          \begin{center}
            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/algorithm1.pdf}
                \caption*{A simple, undirected graph $G$}
              \end{figure}
            \end{textblock*}
          \end{center}
        \end{column}
      \end{columns}
    }

    \only<2-6>{
      \begin{textblock*}{8cm}(8cm, 6cm) % {block width} (coords)
        \begin{center}
          $i= 1$
        \end{center}
      \end{textblock*}
    }

    \only<2>{
      \begin{columns}
        \begin{column}{0.5\textwidth}
          \begin{algorithm}[H]
            \caption*{\textbf{Algorithm} IEDS}
            \scriptsize
            \begin{algorithmic}[1]
            \CSTATE $i \gets 1$
            \CSTATE Remove all isolated paths from $G$
            \While{$G$ is not empty}
              \State $D \gets \emptyset$
              \ForAll{components of $G$}
                \State Pick any vertex $v$
                \State $D \gets D \cup \{ v \}$
                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
                  \State Pick $u$ at distance 3 from some vertex in $D$
                  \State $D \gets D \cup \{ w \}$
                \EndWhile
                \ForAll{$u \in D$}
                  \State Color $u$ with color $i$
                \EndFor
                \State $i \gets i + 1$
                \ForAll{$u \in D$}
                  \State Remove $N(u)$ from $G$
                \EndFor
                \State Remove all isolated paths from G
              \EndFor
            \EndWhile
            \State Color all removed isolated paths using color $i$
            \end{algorithmic}
          \end{algorithm}
        \end{column}
        \begin{column}{0.5\textwidth}
          \begin{center}
            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/algorithm1.pdf}
                \caption*{A simple, undirected graph $G$}
              \end{figure}
            \end{textblock*}
          \end{center}
        \end{column}
      \end{columns}
    }

    \only<3>{
      \begin{textblock*}{8cm}(8cm, 6.5cm) % {block width} (coords)
        \begin{center}
          $D= \{\}$
        \end{center}
      \end{textblock*}

      \begin{columns}
        \begin{column}{0.5\textwidth}
          \begin{algorithm}[H]
            \caption*{\textbf{Algorithm} IEDS}
            \scriptsize
            \begin{algorithmic}[1]
            \State $i \gets 1$
            \State Remove all isolated paths from $G$
            \While{$G$ is not empty}
              \CSTATE $D \gets \emptyset$
              \ForAll{components of $G$}
                \State Pick any vertex $v$
                \State $D \gets D \cup \{ v \}$
                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
                  \State Pick $u$ at distance 3 from some vertex in $D$
                  \State $D \gets D \cup \{ w \}$
                \EndWhile
                \ForAll{$u \in D$}
                  \State Color $u$ with color $i$
                \EndFor
                \State $i \gets i + 1$
                \ForAll{$u \in D$}
                  \State Remove $N(u)$ from $G$
                \EndFor
                \State Remove all isolated paths from G
              \EndFor
            \EndWhile
            \State Color all removed isolated paths using color $i$
            \end{algorithmic}
          \end{algorithm}
        \end{column}
        \begin{column}{0.5\textwidth}
          \begin{center}
            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/algorithm1.pdf}
                \caption*{A simple, undirected graph $G$}
              \end{figure}
            \end{textblock*}
          \end{center}
        \end{column}
      \end{columns}
    }

    \only<4>{
      \begin{textblock*}{8cm}(8cm, 6.5cm) % {block width} (coords)
        \begin{center}
          $D= \{8\}$
        \end{center}
      \end{textblock*}

      \begin{columns}
        \begin{column}{0.5\textwidth}
          \begin{algorithm}[H]
            \caption*{\textbf{Algorithm} IEDS}
            \scriptsize
            \begin{algorithmic}[1]
            \State $i \gets 1$
            \State Remove all isolated paths from $G$
            \While{$G$ is not empty}
              \State $D \gets \emptyset$
              \ForAll{components of $G$}
                \CSTATE Pick any vertex $v$
                \CSTATE $D \gets D \cup \{ v \}$
                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
                  \State Pick $u$ at distance 3 from some vertex in $D$
                  \State $D \gets D \cup \{ w \}$
                \EndWhile
                \ForAll{$u \in D$}
                  \State Color $u$ with color $i$
                \EndFor
                \State $i \gets i + 1$
                \ForAll{$u \in D$}
                  \State Remove $N(u)$ from $G$
                \EndFor
                \State Remove all isolated paths from G
              \EndFor
            \EndWhile
            \State Color all removed isolated paths using color $i$
            \end{algorithmic}
          \end{algorithm}
        \end{column}
        \begin{column}{0.5\textwidth}
          \begin{center}
            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/algorithm1-slide-1.pdf}
                \caption*{A simple, undirected graph $G$}
              \end{figure}
            \end{textblock*}
          \end{center}
        \end{column}
      \end{columns}
    }

    \only<5>{
      \begin{textblock*}{8cm}(8cm, 6.5cm) % {block width} (coords)
        \begin{center}
          $D= \{8\}$
        \end{center}
      \end{textblock*}

      \begin{columns}
        \begin{column}{0.5\textwidth}
          \begin{algorithm}[H]
            \caption*{\textbf{Algorithm} IEDS}
            \scriptsize
            \begin{algorithmic}[1]
            \State $i \gets 1$
            \State Remove all isolated paths from $G$
            \While{$G$ is not empty}
              \State $D \gets \emptyset$
              \ForAll{components of $G$}
                \State Pick any vertex $v$
                \State $D \gets D \cup \{ v \}$
                \CWhile{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
                  \State Pick $u$ at distance 3 from some vertex in $D$
                  \State $D \gets D \cup \{ w \}$
                \EndWhile
                \ForAll{$u \in D$}
                  \State Color $u$ with color $i$
                \EndFor
                \State $i \gets i + 1$
                \ForAll{$u \in D$}
                  \State Remove $N(u)$ from $G$
                \EndFor
                \State Remove all isolated paths from G
              \EndFor
            \EndWhile
            \State Color all removed isolated paths using color $i$
            \end{algorithmic}
          \end{algorithm}
        \end{column}
        \begin{column}{0.5\textwidth}
          \begin{center}
            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/algorithm1-slide-1.pdf}
                \caption*{A simple, undirected graph $G$}
              \end{figure}
            \end{textblock*}
          \end{center}
        \end{column}
      \end{columns}
    }

>>>>

% \algdef{SE}[FOR]{CFOR}{ENDFOR}%
%    [2][default]{\ColorLine\algorithmicfor\ #2\ \algorithmicdo\ALG@compatcomm{#1}}%
%    {\algorithmicend\ \algorithmicfor}%
% \algdef{S}[FOR]{CFORALL}%
%    [2][default]{\ColorLine\algorithmicforall\ #2\ \algorithmicdo\ALG@compatcomm{#1}}%

\algdef{SE}[FOR]{For}{EndFor}[1]{\algorithmicfor\ #1\ \algorithmicdo}{\algorithmicend\ \algorithmicfor}%

\algdef{S}[FOR]{CForAll}[1]{\ColorLine\algorithmicforall\ #1\ \algorithmicdo}%

\algdef{SE}[LOOP]{CLOOP}{ENDLOOP}%
   [1][default]{\ColorLine\algorithmicloop\ALG@compatcomm{#1}}%
   {\algorithmicend\ \algorithmicloop}%
\algdef{SE}[REPEAT]{CREPEAT}{UNTIL}%
   [1][default]{\ColorLine\algorithmicrepeat\ALG@compatcomm{#1}}%
   [1]{\algorithmicuntil\ #1}%
\algdef{SE}[IF]{CIF}{ENDIF}%
   [2][default]{\ColorLine\algorithmicif\ #2\ \algorithmicthen\ALG@compatcomm{#1}}%
   {\algorithmicend\ \algorithmicif}%
\algdef{C}[IF]{IF}{CELSIF}%
   [2][default]{\ColorLine\algorithmicelse\ \algorithmicif\ #2\ \algorithmicthen\ALG@compatcomm{#1}}%
\algdef{Ce}[ELSE]{IF}{CELSE}{ENDIF}%
   [1][default]{\ColorLine\algorithmicelse\ALG@compatcomm{#1}}%
\makeatother
\algtext*{EndWhile}%
\algtext*{EndFor}%

@@

    \input{ieds}
